Building table-like applications using cached data

### 2014-05-04 english_version/IEEE_TKDE/paper_main.tex
domain word added and middle names provided

\author{Sergey~Mosin,
        Sergey~Zykin % <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem S. Mosin, S. Zykin are with the
the Siberian Branch of the Russian Academy of Sciences, Omsk, Russia.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: svmosin@gmail.com, szykin@mail.ru}% <-this % stops a space
\thanks{}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
We primarily address the usage of cached Database query results in our paper.
This problem was already discussed and has some software implementations. In our
work, we propose Truth spaces usage in logical formulas while querying a Database.
This approach is supposed to help an analyst, who works with dynamically built
data representations logically described as multidimensional tables. We consider
queries in a form of relational algebra expressions, similar to "universal
relational query". Logical formulas in the queries are
presented in Disjunctive Normal Form. They consist of atomic expressions
consisting of SQL predicates. In the paper we consider single and multiple table
cases to build new data representations.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.

>>>>

\author{Sergey~Vladimirovich~Mosin,
        Sergey~Vladimirovich~Zykin % <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem S. V. Mosin, S. V. Zykin are
with the the Siberian Branch of the Russian Academy of Sciences, Omsk, Russia.
\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: svmosin@gmail.com, szykin@mail.ru}% <-this % stops a space
\thanks{}}

@@

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
We primarily address the usage of cached Database query results in our paper.
This problem was already discussed and has some software implementations. In our
work, we propose the usage of logical formulas' domain subsets, called Truth
spaces, while querying a Database.
This approach is supposed to help an analyst, who works with dynamically built
data representations logically described as multidimensional tables. We consider
queries in a form of relational algebra expressions, similar to "universal
relational query". Logical formulas in the queries are
presented in Disjunctive Normal Form. They consist of atomic expressions
consisting of SQL predicates. In the paper we consider single and multiple table
cases to build new data representations.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway. In particular, the Computer Society does
% not want either math or citations to appear in the abstract.
